\subsection{Norm Relations in Odd Order Extensions}\label{subsec-odd}

We now prove a result analogous to the previous section, but when $F / \bQ$ is any Galois extension of odd order. %The reason one would expect that our norm relations test never forces rank growth in this case is because root number computations do not, as we now show.

%\begin{lemma}
% Let $F / \bQ$ be an odd Galois extension with $G = \Gal(F / \bQ)$. Then $w(E / \bQ) = w(E / F^H)$ for all $H \leq G$. 
%\end{lemma}

%\begin{proof}
%Consider $H \leq G$ and intermediate field $F^H$. Then $\Ind_H^G \trivial \simeq \trivial \oplus \rho \oplus \rho^*$ for some non self-dual representation $\rho$ of $G$, since the only self-dual representation of an odd-order group is the trivial representation. Therefore by Proposition \ref{compute-root-twist}, $w(E / F^H) = w(E / F)w(E, \rho \oplus \rho^*)$ and $w(E, \rho \oplus \rho^*) = 1$. Hence $w(E / \bQ) = w(E / F^H)$ for all $H \leq G$. 
%\end{proof}

%Therefore once we assume that $\rk E / \bQ = 0$, the parity conjecture tells us that $\rk E / F^H$ is even for all $H \leq G$, which does not force it to be non-zero. 


\begin{thm}\label{odd-exts}
 Let $E / \bQ$ be an elliptic curve, $F / \bQ$ be an extension of odd order with Galois group $G$. 
 
Assume that $E$ has good or multiplicative reduction at $2$ and $3$. 
Take any representation $\rho$ of $G$ with quadratic subfield $\bQ(\sqrt{D}) \subset \bQ(\rho)$ and relation
\begin{equation*}\label{odd-exp} \repnorm{\rho}^{\oplus m} =
 \left(\bigoplus_{\mathfrak{g}\in\Gal(\QQ(\rho)/\QQ)}\rho^{\mathfrak{g}}\right)^{\oplus m }=\bigoplus_i\Ind_{F_i/\QQ}\mathds{1}\ominus\bigoplus_j\Ind_{F'_j/\QQ}\mathds{1}
\end{equation*}
 as in Theorem \ref{thm_positive_rank}. Then
 \[ \frac{\prod_i C_{E/F_i}}{\prod_j C_{E/F_j'}}  \in 
    \begin{cases}
        N_{\bQ(\sqrt{D}) / \bQ}(\bQ(\sqrt{D})^{\times}) & m \ \text{odd}, \\
        (\bQ^{\times})^2 & m \ \text{even}.
    \end{cases} \] 
    In other words, one cannot use Theorem \ref{thm_positive_rank} to conclude that $E / F$ must have positive rank. 
\end{thm}

As in Remark \ref{rephrase-thm}, replacing $\rho$ by the sum of its conjugates by elements of $ \Gal(\bQ(\rho) / \bQ(\sqrt{D}))$, we may assume that $\bQ(\rho) = \bQ(\sqrt{D})$. We take $D \in \bZ \backslash \{0,1 \}$ to be squarefree.

The product of terms we are computing is $C(\Theta)$, where $C \colon \B(G) \to \bQ^{\times}$ is given by $C \colon H \mapsto C_{E / F^H}$, and $\Theta$ is any $\rho$-relation.
We break up the function $C$ into $C = \prod_p C_{\fP \mid p} = \prod_p T_{\fP \mid p} \cdot D_{\fP \mid p}$, ranging over primes $p \in \bQ$,
as defined in Notation \ref{not_contr_fns}.
In Remark \ref{Rem-C-D-loc} we showed that
\begin{equation*}\label{Dp-loc}
C_{\fP \mid p} = (D_p, C_v)
\end{equation*}
where $C_v$ is a function on $\B(D_p)$ sending $H \mapsto C_v(E / F_w^H)$, for $D_p = \Gal(F_w / \bQ_p)$. The following result will allow us to apply some results from $\S$\ref{sec-norm-rels}.

\begin{thm}\label{odd-c-brauer}
    When $D_p$ has odd order, $C_v(\Psi) \in (\bQ^{\times})^2$ for any Brauer relation $\Psi \in \B(D_p)$. 
\end{thm}

\begin{proof}
    This follows from \cite[Theorem 2.47]{reg-const} and \cite[Theorem 3.2  (Tam)]{reg-const}.
\end{proof}

\begin{cor}
It is enough to prove Theorem \ref{odd-exts} when $m$ is the order of $\repnorm{\rho}$ in $\C(G)$. Thus we need to prove that, given any $
\Theta \in \B(G)$ such that $\bC[\Theta] \simeq \repnorm{\rho}^{\oplus m}$, $\Theta$ is a norm relation for the function $C$. 
\end{cor}

\begin{proof}
    Since $\bQ(\rho)$ is quadratic, we have that rational squares are norms from $\bQ(\rho)$. As $G$ is odd, any choice of $D_p$ is odd. It follows from Theorem \ref{odd-c-brauer} that $C(\Psi) \in (\bQ^{\times})^2$ for all Brauer relations $\Psi \in \B(G)$. Therefore by Proposition \ref{min-to-all}, it is enough to prove Theorem \ref{odd-exts} when $m$ is the order of $\repnorm{\rho}$ in $\C(G)$. Then $m$ divides $|G|$, hence is odd.
\end{proof}

Let $\tau$ be the generator of $\Gal(\bQ(\sqrt{D}) / \bQ)$.
Let $\ff$ be the smallest integer such that $\bQ(\sqrt{D}) \subset \bQ(\zeta_{\ff})$. Then $\ff \mid |G|$, hence is odd. By Remark \ref{conductor}, $\ff = |D|$ and $D \equiv 1 \pmod 4$. The following shows that it is only of interest to consider decomposition groups of exponent divisible by $\ff$.

\begin{cor}\label{rational-res-2}
    Let the exponent of $D_p$ be $b$. If $\ff \nmid b$, then $C_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$.
\end{cor}

\begin{proof}
    One has $\bQ(\rho) \subset \bQ(\zeta_b) \implies \ff \mid b$ by minimality of $\ff$. Since $\ff \nmid b$, we have $\bQ(\rho) \not\subset \bQ(\zeta_b)$, so $\bQ(\Res_{D_p} \rho) = \bQ$. The corollary then follows from Proposition \ref{rational-res} and Theorem \ref{odd-c-brauer}, noting that since $\C(D_p)$ is odd, multiplication by $2$ is injective. 
\end{proof}

Fix $\Theta = \sum_i n_i H_i \in \B(G)$ with $\bC[\Theta] \simeq \repnorm{\rho}^{\oplus m}$. We prove that at each prime $p$, $C_{\fP \mid p}(\Theta)$ is the norm of an element of $\bQ(\rho)$.  As observed, this depends on $D_p$ and $I_p$. As we deal with each local factor individually, we argue that one can take $D_p = I_p$.

\begin{lemma}\label{tam-up-to-square}
    Let $E / K$ be an elliptic curve. Let $K' / K$ be an extension of number fields odd degree, unramified at the place $v$ of $K$. Then $C_w(E / K') \equiv C_v(E / K) \mod (\bQ^{\times})^2$ for any place $w$ of $K'$ with $ w \mid v$. 
\end{lemma}

\begin{proof}
This is automatic for good reduction and split multiplicative reduction. It is also clear for non-split multiplicative reduction since the residue degree cannot be even (so the reduction type remains non-split at $w$). For additive reduction, see \cite[Lemma 3.12]{reg-const}.
\end{proof}

\begin{lemma}\label{DeqI}
    At a prime $p$, we may assume that $D_p = I_p$ when computing $C_{\fP \mid p}(\Theta)$. 
\end{lemma}

\begin{proof}
Let $p$ have residue degree $f_p$. Let $L / \bQ$ be a Galois extension of degree $f_p$ with cyclic Galois group, such that $p$ is inert in $L$. Further ensure that $F \cap L = \bQ$. Then $\Gal(FL / L) = G$. Let $F_i = F^{H_i}$ and $L_i = F_i L$.

Let $v$ be a place over $p$ in $F_i$. The extension $L_i / F_i$ is Galois, so $v$ is either split or inert in $L_i$.
We claim that $C_v(E / F_i) \equiv \prod_{w | v} C_w(E / L_i) \mod (\bQ^{\times})^2$. Indeed, the number of terms in the product on the right is odd, and by Lemma \ref{tam-up-to-square} $C_v(E / F_i) \equiv C_w(E / L_i) \mod (\bQ^{\times})^2$. 
Letting $C_{\fP \mid p}'$ be the function on $\B(G)$ defined as in \eqref{not_contr_fns} but with $\bQ$, $F$ replaced by $L$, $FL$, we see that $C_{\fP \mid p}'(\Theta) \equiv C_{\fP \mid p}(\Theta) \mod (\bQ^{\times})^2$. 
Thus it is equivalent to do our computation in $FL / L$, but here $p$ has residue degree $1$.
\end{proof}

To prove Theorem \ref{odd-exts}, we proceed by computing $C_{\fP \mid p}(\Theta)$ for each reduction type.

\subsubsection*{Good reduction}
If $E / \bQ$ has good reduction at $p$, then by Proposition \ref{prop_local_fns}(i), $C_{\fP \mid p} = 1$.

\subsubsection*{Multiplicative reduction}

\begin{lemma}
Let $E / \bQ_p$ have non-split multiplicative reduction. Then $C_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$.
\end{lemma}

\begin{proof}
Since $D_p = I_p$, all primes above $p$ have residue degree $1$. Moreover, the ramification degrees are always odd. Thus by Proposition \ref{prop_local_fns}(iii), $C_{\fP \mid p}  = (D_p, \alpha)$
where $\alpha$ is the constant function on $\B(D_p)$ with $\alpha \in \{1, 2\}$, depending on $v_p(\Delta)$ being even or odd. By Proposition \ref{const-fns}, it follows that $C_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$.
\end{proof}

Now suppose $E / \bQ_p$ has split multiplicative reduction. The reduction type remains split at all places above $p$ within sub-extensions of $F / \bQ$. Let $v_p(\Delta) = n$. Then by Proposition \ref{prop_local_fns}(ii), 
\[ C_{\fP \mid p} = (D_p, D_p, en). \]
Since the $n$ factor is constant, $(D_p, D_p, en)(\Theta) \equiv (D_p, D_p, e)(\Theta) \mod (\bQ^{\times}) ^2$ by Proposition \ref{const-fns} .

We have $D_p = I_p = P_p \ltimes C_l$, where $P_p \triangleleft I_p$ is wild inertia, and $C_l = I_p / P_p$ is the tame quotient. $C_l$ is a cyclic group, with $l \mid p^f - 1 = p - 1$. By Corollary \ref{rational-res-2}, we may consider such $D_p$ with exponent  $p^u l$ for some $u \geq 0$ such that $\ff \mid p^u l$. To compute $C_{\fP \mid p}(\Theta)$, we reduce to the tame quotient.

\begin{lemma}
Let $g \colon \B(C_l) \to \bQ^{\times}$ be defined by $H \mapsto [C_l \colon H] = \dim \bC[C_l / H]$. Let $\Psi = P_p \cdot \Res_{D_p} \Theta / P_p \in \B(C_l)$ Then $(D_p, D_p, e)(\Theta)$ and $g(\Psi)$ differ by a (possible) factor of $p$. 
\end{lemma}

\begin{proof}
%Now, $(D_p, D_p, e)(\Theta)$ is the product of ramification indices at primes above $p$. We separate the $p$-part and tame part of this expression.
Recall that the ramification index of a place $w$ above $p$ corresponding to the double coset $H_i x D_p$ has ramification degree $e_w = \frac{|I_p|}{|H_i \cap I_p^x|} =\frac{|I_p|}{|I_p \cap H^{x^{-1}}|}$.
This is the dimension of the permutation representation $\bC[D_p / D_p \cap H^{x^{-1}}]$.
Let  $D_p \cap H^{x^{-1}} = P' \ltimes C_a$ where $P' \leq P$ and $a | l$. Then the ramification index is $\frac{|P|}{|P'|}\cdot \frac{l}{a}$. 
Taking fixed points under wild inertia, one has the following isomorphism of $D_p$-representations  $$\bC[D_p / D_p \cap H^{x^{-1}}]^{P_p} \simeq \bC[D_p / P_p (D_p \cap H^{x^{-1}})] \simeq \bC[D_p / P_p \ltimes C_a].$$ This permutation representation has dimension $\frac{l}{a}$, so we've killed off the $p$-part. 
Then $$\bC[\Res_{D_p} \Theta]^{P_p} \simeq \left(\Res_{D_p} \rho^{\oplus m} \oplus \tau\left(\Res_{D_p}\rho^{\oplus m}\right)\right)^{P_p},$$
and we can consider these as representations of $D_p / P_p = C_l$.
It follows that $(D_p, D_p, e)(\Theta)$ differs from $g(\Psi)$ up to a (possible) factor of $p$. 
\end{proof}

Now we show that this factor of $p$ is a norm from $\fieldnorm{\rho}$.
Note that if $p = 2$ then $P_p = 1$ since $|P_p| \mid |G|$ which is odd. So we only need to consider this factor of $p$ for $p$ odd.

\begin{lemma}\label{p-norm-odd}
    Let $K = \bQ(\sqrt{D})$, with $\ff$ the smallest positive integer such that $K \subset \bQ(\zeta_{\ff})$. Suppose that $\ff$ is odd. Let $\ff \mid p^u l $, for some odd prime $p$, $u \geq 0$ and $l$ such that $p \equiv 1 \pmod l$. Then $p$ is the norm of an element from $K^{\times}$.
\end{lemma}

\begin{proof}
    Since $\ff$ is odd, one has $D = \prod_{q | \ff} q^*$, the product being taken over primes dividing $\ff$. Note that if $q \not= p$, then since $q \mid l$, we have $p \equiv 1 \pmod l \implies p \equiv 1 \pmod q$. By Corollary \ref{p-one-mod-disc},  $p$ is the norm of a principal fractional ideal of $K$, and by Theorem \ref{p-norm-elem-1} or Theorem \ref{p-norm-elem-2}, it is the norm of an element of $K$.
    %We show that $p$ has residue degree $1$ in the extended genus field $E^{+} = K(\{\sqrt{q^*} \colon q | \ff \})$ of $K$ ({\color{red} cf. appendix}).
    %If $q \not= p$ then $q \mid l$, so $p \equiv 1 \pmod l$. Therefore $p$ splits in any quadratic subfield of $E^{+}$ of discriminant not divisible by $p$. Else, $p$ ramifies in any quadratic subfield with discriminant divisible by $p$. Thus it is clear that $p$ has residue degree $1$ in $E^{+}$, hence also in the genus field $E$, and it follows from theorem \ref{p-principal} that $p$ is the norm of a principal ideal.  Else, we invoke theorem \ref{minus-one-norm}.
\end{proof}

\begin{cor}
Let $E / \bQ_p$ have split multiplicative reduction. Then $C_{\fP \mid p}(\Theta) \in \fieldnorm{\rho}$.
\end{cor}

\begin{proof}
By the previous two results, it is sufficient to show that $g(\Psi) \in \fieldnorm{\rho}$. Let $\phi = (\Res_{D_p} \rho)^{P_p}$, viewed as a representation on $D_p / P_p = C_l$. Then $\Psi$ is a $\phi$-relation. If $\ff \nmid l$ then $\bQ(\phi) = \bQ$. Therefore $\bC[C_l / \Psi] \simeq \phi^{\oplus 2}$, implying that $\Psi = 2\Psi'$ for some $\Psi' \in \B(C_l)$ with $\bC[C_l / \Psi'] = \phi$. Then $g(\Psi) = g(\Psi')^2 \in \fieldnorm{\rho}$. Otherwise, suppose that $\bQ(\phi) = \bQ(\rho)$. It follows from Proposition \ref{index-fn-trivial} that $g(\Psi) \in \fieldnorm{\rho}$.
\end{proof}

\subsubsection*{Additive reduction}

Now suppose that $E / \bQ_p$ has additive reduction. In this case, assume that $p \geq 5$
Write $D_p = \Gal(F_w / \bQ_p)$ for $w \mid p$ a place of $F$.

Again we have $D_p = P_p \ltimes C_l$ with $ l \mid p - 1$, and may assume that $\ff \mid p^u l$ where $p^u l $ is the exponent of $D_p$ by Corollary \ref{rational-res-2}. Let $n = v_p(\Delta_E)$. 

We will compute $D_{\fP \mid p}(\Theta)$ and $T_{\fP \mid p}(\Theta)$ separately. 
By Proposition \ref{prop_local_fns}(iv), (v)
\[ D_{\fP \mid p} = 
    \begin{cases}
        (D_p, D_p,\ p^{\floor{e_ /2}}) & \text{if } E / \bQ_p \text{ has potentially multiplicative reduction}, \\
        (D_p, D_p,\ p^{\floor{en /12}}) & \text{if } E / \bQ_p \text { has potentially good reduction}.
    \end{cases}
    \]
In either case, $D_{\fP \mid p}(\Theta) \in N_{\bQ(\rho) / \bQ}(\bQ(\rho)^{\times})$. Indeed, this takes values $1$ or $p$ in $\bQ^{\times} / (\bQ^{\times})^2$. But $p$ is a norm from $\bQ(\rho)$ by Lemma \ref{p-norm-odd}.

%\[ \left|\frac{\Delta_{E}}{\Delta_{E, w}^\min} \right|_w = p^{f_w 12 \cdot \floor{e_w n / 12}} \implies 
%       \left|\frac{\omega}{\omega_{w}^\min} \right|_w = p \]
\vspace{1em}

To compute $T_{\fP \mid p}(\Theta)$, since $p \geq 5$ we may write $E / \bQ_p$ as $E \colon y^2 = x^3 + A x + B$ and use the description from \cite{reg-const} for computing Tamagawa numbers, as detailed in Lemma \ref{tamagawa-num}. The discriminant of $E / \bQ_p$ is $\Delta = -16(4A^3 + 27 B^2)$. The case of potentially multiplicative reduction is almost immediate:

\begin{lemma}[Potentially multiplicative reduction]
    If $E / \bQ_p$ has reduction type $\I_{n}^{*}$ then $T_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$. 
\end{lemma}

\begin{proof}
Since we assume $D_p = I_p$, i.e. the residue degree is one, it follows that any subextension $L'$ of $F_{w} / \bQ_p$ satisfies $\sqrt{B} \in L' \iff \sqrt{B} \in \bQ_p$ and $\sqrt{\Delta} \in L' \iff \sqrt{B} \in \bQ_p$. 
Therefore $T_{\fP \mid p} = (D_p, \alpha)$ where $\alpha \in \{2, 4\}$ by Lemma \ref{lem_add_tam}. But then $(D_p, \alpha)(\Theta) \in (\bQ^{\times})^2$ by Proposition \ref{const-fns}.
\end{proof}

Now suppose that $E / \bQ_p$ has potentially good reduction. Recall from Lemma \ref{lem_add_tam} that if $L' / \bQ_p$ has ramification degree $e$, then the Kodaira type of $E / L'$ depends on $\gcd(e n, 12)$. Thus in a ramified extension of degree coprime to $12$, the Kodaira type is unchanged, and further if this extension is totally ramified (so the residue degree is $1$), the Tamagawa number is unchanged also. Thus when $3 \nmid |D_p|$, $T_{\fP \mid p} = (D_p, \alpha)$ for some constant $\alpha$. If we have type $\III$ or $\III^*$ or $\I_0^*$ then the Tamagawa number is still unchanged in any totally ramified extension of odd degree extension, even when the degree is divisible by $3$. Then the Proposition \ref{const-fns} implies the following lemma:

\begin{lemma}
    \
    \begin{enumerate}[(i)]
        \setlength\itemsep{0em}
        \item If $E / \bQ_p$ has potentially good reduction and $3 \nmid |D_p|$, then $T_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$.
        \item If $E / \bQ_p$ has potentially good reduction of type $\III$, $\III^*$, or $\I_0^*$, then $T_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$.
    \end{enumerate}
\end{lemma}

Thus we assume that $3 \mid |D_p|$. Since we assumed $p \geq 5$, we have $D_p = I_p = P_p \ltimes C_l$ with $3 \mid l$ and $p \equiv 1 \pmod l$.

\begin{lemma}
If $E / \bQ_p$ has Type $\II$ or Type $\II^*$ additive reduction and $3 \mid |D_p|$, then $T_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$. 
\end{lemma}

\begin{proof}
If $3 \mid |D_p|$ then there is a subextension $F'$ of $F_w / \bQ_p$ with $\Gal(F_w / F') = C_3$. Then Lemma \ref{lem_nottwo} implies that $\sqrt{\Delta} \in F'$. But $F' / \bQ_p$ has residue degree $1$, hence $\sqrt{\Delta} \in \bQ_p$. 

If $L' / \bQ_p$ is an odd degree extension that is divisible by $3$, then $E / L'$ has reduction type $I_0^*$. By Lemma \ref{tamagawa-num} the Tamagawa number of $E / L'$ is $2$ if $\sqrt{\Delta} \not\in \bQ_p$ and $1$ or $4$ if $\sqrt{\Delta} \in \bQ_p$. Therefore the Tamagawa number will be $1$ or $4$, which is a square.
On the other hand if $L' / \bQ_p$ is an extension of odd degree then the reduction type over $L'$ is $\II$ or $\II^*$ and the Tamagawa number is $1$. It follows that $T_{\fP \mid p}(\Theta)$ is a product of square terms, so is itself square.  
\end{proof} 

Now, if $E /\bQ_p$ has additive reduction of type $\IV$ or $\IV^*$, it attains good reduction over any totally ramified cyclic extension of degree divisible by $3$. This could result with $3$ coming up an odd number of times in $T_{\fP \mid p}(\Theta)$, when $\sqrt{B} \not\in \bQ_p$. 
%We show that for both types, one has $\sqrt{B} \in \bQ_p$. 
%Indeed, if $\delta = 4$, then $v_p(B) = 2$, and $v_p(A) \geq 2$. 
%\vspace{1em}
%In summary, 
%\begin{equation}
 %   \prod_{d ' \mid d} C(E / F_{\fp}^{D_{d'}})^{\mu(d / d')}
  %  = 
   % \begin{cases}
    %    1 & 3 \nmid d, \\
    %   1 & 3 \mid d, \delta \in \{0, 3, 6, 9\}, \\
    %    1 \cdot \square & 3 \mid d, \delta \in \{2, 10\}, \\
    %    3^a \cdot\square, a \in \{0,1\} & 3 \mid d, \delta \in \{4,8\}.
    %\end{cases}
%\end{equation}
%\begin{rem}
%   There's no reason why we can't get 3; see elliptic curve 441b1 with additive reduction at $7$ of type IV and Tamagawa number equal to $3$
%\end{rem}

%\textbf{If $D_p = C_l$ then we are able to finish our argument.} As in the proof of Proposition \ref{semi-stable-gd}, there exists $a_{l'} \in \bZ$ such that $\Res_{D_p}\Theta = \sum_{l' \mid l} a_{l'} \Psi_{l'}$ where $\Psi_{l'} \in \B(G)$ is such that $\bC[\Psi_{l'}] \simeq \chi_{l'}$, as in Example \ref{cyclic-relns}.

Recall from the proof of Proposition \ref{const-fns} that $\Res_{D_p} \Theta = \sum_i n_i \sum_{x \in H_i \backslash G / D_p} D_p \cap H^{x^{-1}}$, with $\sum_i n_i | H_i \backslash G / D_p|$ even. If $D_p = \Gal(F_w / \bQ_p)$, then the number of subextensions divisible by $3$ (i.e. the number of subextensions where we obtain good reduction ) corresponds to the number of subgroups with index divisible by $3$ in $\Res_{D_p}\Theta$. We compute this number to determine $\ord_3(T_{\fP \mid p}(\Theta))$ modulo squares.

Similarly to the split multiplicative case, we may pass to the tame quotient $C_p / P_p = C_l$. Indeed 

\[ 3 \mid  [D_p : D_p \cap H^{x^{-1}}] = \dim \bC [ D_p / D_p \cap H^{x^{-1}}] \iff 3 \mid \dim \bC[ D_p / D_p \cap H^{x^{-1}} ]^{P_p},\] 
since $3 \nmid|P_p|$. Therefore we may compute the number of subgroups divisible by $3$ in $\Psi = P_p \cdot \Res_{D_p} \Theta / P_p \in \B(C_l)$.  Let $h \colon \B(C_l) \to \bQ^{\times}$ be the function given by $H \mapsto \begin{cases} 3 & 3 \mid [C_l : H], \\ 1 & 3 \nmid [C_l : H]. \end{cases}$

\begin{prop}
   Suppose that $E / \bQ_p$ has additive reduction of Type $\IV$ or $\IV^*$, with $c_v(E / \bQ_p) = 3$.  Then $T_{\fP \mid p}(\Theta) \equiv h(\Psi) \mod (\bQ^{\times})^2$ and $T_{\fP \mid p}(\Theta) \in \fieldnorm{\rho}$. 
\end{prop}

\begin{proof}
The fact that $T_{\fP \mid p}(\Theta) \equiv h(\Psi) \mod (\bQ^{\times})^2$ has been observed above.
Let $\psi_3$ be an irreducible character of $D_p$ of order $3$. One has that $ \langle \Ind_{C_{l / l'}}^{C_l} \trivial , \psi_3 \rangle =  1$ when $3 \mid l'$ and is zero when  $3 \nmid l'$. 
Thus $$h(\Psi) = 3^{\langle \bC[C_l / \Psi], \psi_3 \rangle}.$$ As in the proof of Proposition \ref{index-fn-trivial}, write $\bC[C_l / \Psi] = \sum_{l' \mid l} a_{l'} \chi_{l'}$, where $\chi_{l'}$ is an irreducible rational character, of $C_l$ with kernel of index $l'$. Observe that $\langle \chi_{l'}, \psi_3 \rangle = 0$ unless $l' = 3$, in which case it is $1$. Therefore $h(\Psi) \equiv 3^{a_3} \mod (\bQ^{\times})^2$. In the proof of Proposition \ref{index-fn-trivial}, we showed that $a_3$ is even unless $\ff \mid 3$,  i.e. that $\bQ(\rho) = \bQ(\sqrt{-3})$. But then $3$ is a norm in $\bQ(\rho)$. Thus we see that in all cases $T_{\fP \mid p}(\Theta) \in N_{\bQ(\rho) / \bQ}(\bQ(\rho)^{\times})$. 
\end{proof}

We have observed that for all reduction types of $E / \bQ_p$, one has $C_{\fP \mid p} (\Theta) \in \fieldnorm{\rho}$, and so $C(\Theta) \in \fieldnorm{\rho}$, completing the proof of Theorem \ref{odd-exts}.

\qed

%\begin{cor}\label{cor-odd-decomp}
%    Let $G$ be a finite group, $\rho$ a character of $G$ with $\bQ(\rho)$ quadratic. Let $\Theta \in \B(G)$ be a $\rho$-relation. If $D_p \leq G$ is of odd order, then $C_{\fP \mid p}(\Theta) \in \fieldnorm{\rho}$.
%\end{cor}

%\begin{proof}
%If $\rho$ has even order in $\hat{C}(G)$ then $\bigoplus_{\fg  \in G} $
\begin{cor}\label{cor-odd-decomp}
Let $E / \bQ$ be an elliptic curve, $F / \bQ$ a Galois extension with Galois group $G$. Assume that $E$ has good or multiplicative reduction at $2$ and $3$. 

Consider $\rho$ a character of $G$. Let $\Theta$ be a $\rho$-relation, with $\bC[G / \Theta] \simeq \repnorm{\rho}^{\oplus m}$, $ m \geq 1$. Let $D_p \leq G$ be of odd order. 
If $m$ is even, $C_{\fP \mid p}(\Theta) \in (\bQ^{\times})^2$. Else, $C_{\fP \mid p}(\Theta)$ is the norm of an element of every quadratic subfield of $\bQ(\rho)$. 
\end{cor}

\begin{proof}
    This result essentially follows from Proposition \ref{prop-restrict-decomp}. Recall that $C_{\fP \mid p} = (D_p, C_v)$ by Remark \ref{Rem-C-D-loc}, and if $D_p$ is odd, then $C_v\left(\Psi\right) \in (\bQ^{\times})^2$ for all Brauer relations $\Psi \in \B(D_p)$ by Theorem \ref{odd-c-brauer}. In addition $\hat{C}(D_p)$ is of odd order. 

    Taking restriction, one has $\bC[D_p / \Res_{D_{p}} \Theta] \simeq \repnorm{\Res_{D_p} \rho}^{\oplus m \cdot [\bQ(\rho) \colon \bQ(\Res_{D_p} \rho)]}$. If $m$ is even then $C_{\fP \mid p}(\Theta) = C_v(\Res_{D_p} \Theta) \in (\bQ^{\times})^2$, since there exists some $(\Res_{D_p} \rho)$-relation $\Theta' \in \B(D_p)$ with $\bC[D_p / 2 \Theta'] \simeq \bC[D_p / \Res_{D_p} \Theta]$. 

    Else, by Theorem \ref{odd-exts}, $C_v(\Theta')$ is a norm from every quadratic subfield of $\Res_{D_p} \rho$ for every $\left(\Res_{D_p} \rho\right)$-relation $\Theta'$. The result follows by the statement of Proposition \ref{prop-restrict-decomp}. 
\end{proof}

